Residence time, a master variable for a more temporal ecology

### 2015-06-20 paper/Manuscript.Rmd
finishing up Results -KL

@@

*Growth rate vs. maintenance—*A large literature suggests increasing selection for quickly growing and reproducing organisms as residence time decreases. But, as residence time decreases, selection on rapid growth and reproduction should lessen with respect to selection on a low-cost of maintenance and the ability to persist in the face of low resource supply. However, organisms that can quickly consume resources, grow, and reproduce, could continue to dominance if they can keep maintenance costs down.

*Attachment vs. motility—*Attachment and motility have clear costs and benefits. Motility allows organisms to seek out resources, refuge, and mates, while attachment allows weakly dispersing organisms to resist being carried away. However, structures required for motility and attachment are not energy-free and presumably come at an energetic cost.

@@

We used a stochastic individual-based model that simulated a wide array of environmental and ecological conditions and species-level and individual-level traits. As much of this variation as possible was assigned at random, to explore a large swath of multi-parameter space. Rather than examine the independent influence of each of these factors, our purpose was to find whether simple relationships of residence time to total abundance and community-level characteristics should hold in ecologically complex conditions.

The random selection of trait values of new species (whether immigrating or evolving) allowed realistic and unreasonable trait combinations to occur. For example, a species requiring little maintenance but capable of rapid growth was possible. However, the trait combinations that persisted in the model were realistic combinations of traits that point to life history trade-offs.

>>>>

*Richness, evenness, rarity, and dominance*—As expected and as shown in many previous studies, *S* shared a power-law-like relationship with *N*, i.e., *S* = *cN*$^{z}$, where z ~ 0.5, revealing that the model generated a realistic dynamic whether including or excluding immigration and speciation and whether reproduction was sexual or clonal, and whether movement was fluid, random, or environmentally correlated. As predicted, the relationship of *S* to $\tau$ followed a hump-shaped relationship. Also as predicted, greater *N* lead to greater rarity, greater dominance, and less evenness, regardless of the model specifics.

*Species turnover*—We observed a monotonically decreasing relationship $\beta$-diversity to $\tau$, when calculated as species turnover (presence/absence).

@@

*Growth rate vs. maintenance—*Increasing residence time lead to a strong power-law decrease in maintenance, revealing strong selective pressure to evolve low maintenance costs in resource limited environments of low turnover.

@@

We used a stochastic individual-based model that simulated a wide array of environmental and ecological conditions and species-level and individual-level traits. As much of this variation as possible was assigned at random, to explore a large swath of conditions and parameter space. Rather than examine the independent influence of each of these factors, our purpose was to find whether previously known and novel relationships of residence time to total abundance and community-level characteristics should hold in ecologically complex systems and characteristically different environments.

...
